Nitric oxide feedback to ciliary photoreceptor cells orchestrates UV avoidance

### 2023-06-02 Manuscript/Manuscript.Rmd
Ms: discussion edit, gravity section

The only motor output of the cPRC circuit in the wiring diagram is the prototroch ciliary band postsynaptic to the MC and Ser-h1 ciliomotor neurons. Our Ca2+-imaging data revealed a late NO-dependent inhibition of Ser-h1 and activation of the MC cell suggesting the inhibition of ciliary beating [@veraszto2017].

>>>>

The only motor output of the cPRC circuit in the wiring diagram is the prototroch ciliary band postsynaptic to the MC and Ser-h1 ciliomotor neurons. Our Ca2+-imaging data revealed a NO-dependent inhibition of Ser-h1 and activation of the MC cell suggesting the inhibition of ciliary beating [@veraszto2017].
